### 2017-07-14 background.tex
Adding stuff

\section{Backgrouond and Motivation} \label{sec:background}

@@

>>>>

\section{Background and Motivation} \label{sec:background}

@@

Formal privacy techniques such as homomorphic encryption, secure multiparty computation and
other cryptographic solutions for protecting private data often comes at heavy computational
overheads \cite{naehrig2011can}. Work on database based solutions \cite{popa2011cryptdb}
demonstrates the need for matching the privacy protecting methods to the analysis in question
to reduce overheads. The majority of the work in this area is focussed on the security of
numerical data, while the data we are dealing with is mostly large volumes of textual data.
Recent work \cite{kepner2014computing} on applying privacy techniques to securely compute
mathematical operation at big data scales incur a 2x overhead.

Computing systems in some of the most critical and sensitive areas such as military, avionics,
nuclear are protected from intrusion by physical isolation\cite{byres2013air}, \cite{ross2013security}.
The US census bureau to this day has several enclaves that host sensitive microdata accessible
only on site \cite{rdc_uscensus}. With physical proximity being a limiting factor, data enclaves
evolved to support network access via encrypted channels and limited IO bandwidths \cite{lane2008using}, \cite{grossman2016toward}.
Accessibility in this case comes at the cost of increased attack surface.

On Cloud Kotta we currently archive over 10TB of compressed text data and in the past year
alone, analyses on the datasets consumed over 0.25M core hours. With a cloud hosted system
such as our
